A fast and memory-efficient transition state search method for complex energy landscapes

### 2022-05-09 manuscript.tex
Added bracketing figure

The BITSS potential in \cref{eq:bitss} and iterative steps above offer key advantages over existing bracketing methods that also use two states to locate the transition state.
Two such methods are the Step and Slide method \cite{Miron2001} and the saddle method \cite{Dewar1984}.
In the the Step and Slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
Conversely in the saddle method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated in the SI.
The BITSS method is more reliable, as principally the image pair can both approach the transition state from below, and descend down a ridge from above.

>>>>

\subsection{Other bracketing methods}
\begin{figure}[htb]
  \includegraphics[width=\linewidth]{bracketing.pdf}
  \caption{\label{fig:bracketing}
    Trajectories of the bracketing methods on a hooked potential with a single saddle point.
    The minimum energy pathway is shown by the dashed line.
  }
\end{figure}
The BITSS potential in \cref{eq:bitss} and iterative steps above offer key advantages over existing bracketing methods that also use two states to locate the transition state.
Two such methods are the Step and Slide method \cite{Miron2001} and the saddle method \cite{Dewar1984}.
In the the Step and Slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
Conversely in the saddle method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated in the SI.
The BITSS method is more reliable, as principally the image pair can both approach the transition state from below, and descend down a ridge from above.
